Probabilistic Symbol Encoding for \\Convolutional Associative Memories

### 2017-01-19 papers/hrr-paper/paper.tex
Switch to conference LaTeX template

\documentclass[conference]{IEEEtran}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{\IEEEauthorblockN{Igor Peric, Alexandru Lesi, Daniel Spies, Stefan Ulbrich, Arne R{\"o}nnau, Marius Z{\"o}llner, R{\"u}diger Dillman}
		\IEEEauthorblockA{FZI Forschungszentrum Informatik\\
			Karlsruhe, Germany\\
			Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de}
	}

>>>>

\documentclass[journal]{journal}
% Some Computer Society conferences also require the compsoc mode option,
% but others use the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

@@

	% author names and affiliations
	% use a multiple column layout for up to three different
	% affiliations
	\author{Igor~Peric, Alexandru~Lesi, Daniel~Spies, Stefan~Ulbrich, Arne~R{\"o}nnau, Marius~Z{\"o}llner, R{\"u}diger~Dillman\\
		FZI Forschungszentrum Informatik, Karlsruhe, Germany\\
		Email: $\{$peric, lesi, spies, ulbrich, roennau, zoellner, dillmann$\}$@fzi.de
	}
